\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{hyperref}
\title{Image Classification with Vision Transformers: An Experimental Study}
\author{Your Name Here}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This is a placeholder document describing the experimental setup and findings for the CIFAR-100 Vision Transformer assignment. Replace the placeholder text with your full analysis once experiments have completed.
\end{abstract}

\section{Introduction}
Provide context on the CIFAR-100 dataset, the motivation for using Vision Transformers, and a short summary of related work.

\section{Methodology}
\subsection{Data Preparation}
Document the preprocessing pipeline including resizing, augmentation, and the train/validation split strategy.

\subsection{Model Architecture}
Detail the ViT-B/16 backbone, classification head, initialization, and any architectural modifications.

\subsection{Training Procedure}
Summarize the loss, optimizer, scheduler, learning rate warmup, batch size, and total epochs. Include justification for each choice.

\section{Results}
\subsection{Quantitative Metrics}
Report accuracy, precision, recall, F1 score, ROC-AUC (one-vs-rest), and present the confusion matrix.

\subsection{Qualitative Analysis}
Discuss representative misclassifications and trends observed in the per-class performance.

\section{Discussion}
Reflect on lessons learned, limitations, and future work.

\section{Conclusion}
Offer final thoughts and summarize the contribution of the assignment deliverable.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
